---
title: "tt3"
author: "Palma"
date: "10/4/2021"
output: html_document
---

## Tidy Tuesdsay #3


```{r}
library(ggplot2)
library(dplyr)
library(tidyverse)
library(tidytuesdayR)
library(rvest)
```

```{r}
tuesdata <- tidytuesdayR::tt_load('2021-09-21')

nominees <- tuesdata$nominees
```


```{r}
nominees_new <- 
  nominees %>%
  select(-logo, -page_id, -page)
```

```{r}
nominees_new
```
```{r}
nominees_netflix <- nominees_new %>%
  filter(distributor == "Netflix")
```




```{r}
Netflix_graph <- nominees_netflix %>%
    ggplot(aes(x = year)) +
    geom_histogram(stat = "count", fill = "#Aa1d1d") +
    facet_wrap(~type) +
  labs(x = "Count", y = "Year", title = "Netflix's Emmy Award Nominations Compared with Wins Over the Years", subtitle = "by Anthony Palma") 
```

```{r}
Netflix_graph +
   theme(panel.background = element_rect(fill = "#000000"), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        plot.background = element_rect(fill = "#Aa1d1d"), 
        text = element_text(color = "#FFFFFF"), 
        axis.text = element_text(color = "#FFFFFF"))
```

**Question:  What does Netflix's Emmy Award performance look like over the years?**

Netflix is my favorite streaming platform which has had dozens of major hits over the last couple years.  I was curious as to how their rise in binge-worthy shows over the pandemic would be reflected in a faceted graph looking at nomination and winner of category counts for their shows. To no surprise, their content quality increased as I perceived, which can be seen with the rapid rise in emmy nominated shows, peaking during the 2020 pandemic year (Note: 2021 was still very strong though).  Surprisingly, their winner of category graph doesn't actually peak where their nominations graph does....the winner graph peaks just a bit after in 2021.  This could be because some of the backend quality 2020 films/shows were after the 2020 awards or it also could be because Netflix limited production to just their top hits in 2021 maximizing performance of shows and minimzing loss in a tough economic situation...
